\LARGE BAND\\ \Large Unleashing Tokenized Economy

### 2018-03-26 paper.tex
Bump version: 0.1.3
Add Client Layer section

\title{\LARGE BAND\\
    \Large Unleashing Tokenized Economy}
\author{
        Soravis Srinawakoon\\
        \small\href{mailto:soravis@bandprotocol.com}
            {\nolinkurl{soravis@bandprotocol.com}}
    \and
        Sorawit Suriyakarn\\
        \small\href{mailto:swit@bandprotocol.com}
            {\nolinkurl{swit@bandprotocol.com}}
    }
\date{\today\\\small Draft Version 0.1.2}
\begin{document}

@@

\section{Client Layer}

\subsection{Campbase}

\subsection{Problem Definition}

\subsection{Solution}

\subsubsection{Story Feed}

\subsubsection{Fan Feed}

\subsubsection{Event}

\subsubsection{Subscription}

\subsubsection{Store}

\subsection{Community Manager}

\subsection{Consumers}

>>>>

\title{\LARGE BAND\\
    \Large Unleashing Tokenized Economy}
\author{
        Soravis Srinawakoon\\
        \small\href{mailto:soravis@bandprotocol.com}
            {\nolinkurl{soravis@bandprotocol.com}}
    \and
        Sorawit Suriyakarn\\
        \small\href{mailto:swit@bandprotocol.com}
            {\nolinkurl{swit@bandprotocol.com}}
    }
\date{\today\\\small Draft Version 0.1.3}
\begin{document}

@@

\section{Client Layer}
One of the main roadblocks of cryptocurrency's mass adoption is usability. Non-technical users struggle to understand and interact directly with blockchain layer and public-private keys. User-friendly applications are necessary to bring benefit of BAND Protocol to general mass consumers even if they are not familiar with its technical aspect. Campbase will be the first consumer application developed in conjunction with BAND Protocol. Since BAND Protocol is an open, permissionless blockchain protocol, anyone can build client application on top of the protocol.

\subsection{Campbase}
Campbase is the first tokenized marketplace centered around celebrities in the creative industry. In particular, Campbase targets individuals in the following creative economy: music, art, film, publishing, and sport. As individuals in the creative industry tend to gather loyal followers, they are apt to be among the early adopter of the platform as they have a new way to connect and monetize their large fan base.

\subsection{Problem Definition}
Current creative industry is facing a monetization problem as it becomes increasingly harder for them to directly sell their original content. Publishers and content distributors are two big middlemen who take big cut of the profit created by individual. With the emergence of Internet technology, platform companies are bringing in huge revenue while original content providers or celebrities receive little share of the revenue. For example, musician receives less than one cent per play on Spotify which unsurprisingly leads to ongoing feud between streaming service and artists~\cite{taylorswiftspotify, jayzspotify}. Similarly, famous celebrities amass millions of followers on content platform such as Facebook, Instagram and Twitter but they receive tiny share of the advertising revenues from these content aggregating platforms. Facing such issue, many celebrities turn to advertising model where third party companies pay celebrities to advertise company's products. This practice leads to misleading information for consumers as those sponsored advertisements are not truly transparent and are often masked as an endorsement of the celebrities. For example, a recent dispute on social media exposed one social media celebrity who demanded a luxurious Dubin hotel to give her free accommodation in exchange for free exposure on Instagram to her 80,000 followers. This sparks debate around the moral and ethical implication of how celebrities use their fame to promote products inorganically and mislead their followers~\cite{dublinban, hotelban}. There should be a new way for artists and content provider to monetize their products and services. Most importantly celebrities should be able monetize their own fan base while keeping incentives aligned with their followers.

\subsection{Solution}
Campbase will be the first decentralized platform for celebrities in creative industry to monetize their followers. As Taylor Swift aptly said: “music is art, and art is important and rare. Important, rare things are valuable. Valuable things should be paid for.”~\cite{taylorswiftspotify}

Campbase allows celebrities to monetize their rare attention and sell their products on a blockchain-based social platform. In particular, Campbase has five main features for each community which are described in the subsequent sections:
\begin{itemize}
\setlength\itemsep{0em}
\item Story Feed
\item Fan Feed
\item Event
\item Subscription
\item Store
\end{itemize}

%(pictures of ui/ux)

Celebrities will use Campbase to issue their unique Community Token which links to the overall value of their community. Community Token will be used as a primary currency in the community, as a stake to subscribe to discounts and other benefits customized by Community Manager and as a main token to buy attention and curate the community. As more consumers follow the community and stake their Community Tokens to receive discounts, they will be incentivized to spend those discounts and purchase more goods and services. In turn, more economic activities drive larger discount for loyal token holders. Positive feedback loop generates greater demand for followers to obtain Community Token and become part of loyal community. Both celebrities and followers can benefit from this tokenized economy and curation market.

\subsubsection{Story Feed}
Story Feed is the main content page curated by Community Manager. Community Manager can share text-based posts, images, or videos to their followers similar to typical social media platform. Followers can interact with their Community Manager by posting comments. Campbase creates attention curation market by allowing followers to vote on comments using Attention Token bought from the store with their Community Token. Most voted comments in each post will be shown on the feed so that Community Manager can easily interact with loyal followers. As Community Manager grows in popularity and more loyal followers demand his or her attention, the more Attention Token they are willing to pay and vote for their comments. This dynamic creates a new revenue stream for Community Managers. Since their attention is rare, their attention will become a new valuable in the tokenized economy.

\subsubsection{Fan Feed}
Fan Feed is the secondary content page curated by the community. Community members can post their own image, preferrably related to the community topic such as their pictures with Community Manager. They can similarly vote and interact with each other via comment section. Community Manager also has incentive to interact with the community through the Fan Feed to keep community more engaging. The more interaction is desired by community member, the more valuable the attention is.

\subsubsection{Event}
Community Manager in the creative industry is likely to hold multiple events such as concert, meet \& greet, autograph event, etc. Event tab will organize all relevant events held by Community Manager so that their followers can easily follow their schedule. Community Manager can also directly monetize their event by selling entrance ticket through the application.

\subsubsection{Subscription}
Subscription tab allows community manager to create their own subscription business model. Individuals in the creative industry produce many non-rivalrous goods which is suitable for a subscription model. For example, distributing book content to one consumer does not prevent another consumer to receive the same book content and the cost to providers is close to zero for each additional unit. This allows people to stake their Community Token and receives continuous benefits by being part of the loyal followers.

\subsubsection{Store}
Store has two main components: official store and P2P marketplace.

In the official store, consumers buy products and services in the form of Product Token directly from Community Manager. Community Managers can customize their product token and associated offers however they wish. Consumers can purchase product token using their Community Token directly in the official store.

In the P2P marketplace, consumers are able to list their product token and the price they want to sell at if the product token is tagged \textit{sellable} by Community Manager. Marketplace allows much better liquidity and transparency than traditional P2P market. For example, selling Concert Ticket Token on P2P marketplace ensures that the Concert Ticket Token is not a counterfeit while everyone in the community can easily browse through the marketplace, instead of on a third-party platform or in the physical world. It also allows Community Manager to profit from resellers as part of reseller's revenue can be configured to go directly to Community Manager’s beneficiary address.

\subsection{Community Manager}
After consulting with many creative publishers such as musicians, writers and artists, it is ostensibly clear that they need a new monetization channel for their content. Campbase will allow these creative publishers to create a new tokenized economy and bring in extra revenues.
\newline
\newline
Benefits to Community Manager include:
\begin{itemize}
\item Able to monetize their attention by curating their own community and respond to loyal fans who are willing to pay for their attention.
\item Able to directly monetize their traditional products and services on a unified social platform.
\item Able to offer new digital products such as rare digital collectibles related to the Community Manager. For example, a rare digital card collection, rare sticker pack which can be used to decorate customer’s picture on a feed, rare theme to be used inside the application, etc.
\item As more consumers participate in the tokenized economy, value of Community Token should rise in proportion to the total network value as consumers purchase more Community Token to receive continuous discounts and subscription benefits offered by the Community Manager.
\item Easy to bootstrap network effect and create loyal fan base for new individuals. Community Token incentivizes followers to curate the community and spread the attention of the community to wider audiences. Incentive is fully aligned between Community Manager and followers.
\end{itemize}

\subsection{Consumers}
Campbase similarly offer benefits to consumers compared to traditional platform as it becomes an all-in-one unified social media and marketplace. Traditionally, channels to follow their favorite celebrities are fragmented. Instagram provides picture feed, while event is often curated in a fragmented forum and official store is rarely formalized unless the celebrities are world-famous. Most simply lack the scale to operate their own store, website and social medias in one platform which makes it very difficult for consumers to follow their favorite celebrities. Campbase is an all-in-one platform for consumers to interact with their favorite celebrities while having an indirect incentive to promote the growth of the community.
\newline
\newline
Benefits to consumers include:
\begin{itemize}
\item Convenient access to follow their favorite celebrities.
\item New channel to interact directly with celebrities, which are very rare in traditional social media. This creates new connection as consumers are able to feel they are real and valuable part of the community. Community Tokens signify a loyal membership symbol.
\item Able to participate in celebrities' success. If consumers believe that the community will grow in the future, consumers can buy Community Token and subscribe to benefits and continuous discounts offered by the platform.
\item More transparent and liquid marketplace for official products. If consumers decide that they may not go to concert, they can easily list and sell through the P2P marketplace. Similarly, buyers can be sure they are getting the real product as Product Tokens are not forgeable.
\end{itemize}
